Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-01 paper.tex
Add comment about PISO-SIMPLE algorithm
Software -> solver
Remove paragraph about free stream nuTilda since these guidelines were not used

\subsection{Software}

Simulations were run using the \textit{pimpleDyMFoam} solver from the
open-source finite volume CFD package \textit{OpenFOAM}, version 2.3.x.

@@

For the SA model, the turbulence transport variable $\tilde{\nu}$, is ideally
zero in the free stream \cite{Spalart1992}, though others recommend using
$\tilde{\nu}/\nu \approx 3$--$5$ for fully turbulent simulations
\cite{Spalart2007}.

>>>>

\subsection{Solver}

Simulations were run using the \textit{pimpleDyMFoam} solver from the
open-source finite volume CFD package \textit{OpenFOAM}, version 2.3.x.
\textit{pimpleDyMFoam} uses a hybrid PISO-SIMPLE algorithm for pressure-velocity
coupling and is compatible with dynamic meshes.

@@
